### 2018-04-13 paper/appendix.tex
one pass for approach
add the rough proof

>>>>

\section{Proof of the upper bound of $\solvecdd$ is coNP}
\label{app:solve-cp}
The following is a proof of \autoref{thm:solve-cp}.
%
In this section, we give a proof that the upper bound of $\solvecdd$ is coNP.
%
It is easy to see that $\prectr$ and $\postctr$ construct the formula as the linear size
of the whole CHC system, and with satisfiability problem in NP for linear arithmetic.
%
$\solvecdd$ at most issues linear number of interpolation queries in terms of number of predicate.
%
Therefore, the upper bound of $\solvecdd$ is coNP.

### 2018-04-13 paper/overview.tex
add the rough proof

The hierarchy of discussed classes of recursion-free systems is
depicted in \autoref{fig:hierarchy}.
%
As shown, the class of CDD systems is a superclass of both the class
of body-disjoint systems and the class of linear systems. So any
recursion-free system that is efficiently expressible in body-disjoint
or linear form is also efficiently expressible in CDD form.
%
In addition, some systems which are expensive to express in
body-disjoint or linear form are efficiently expressible in CDD form.
%
\sys~takes advantage of this fact when solving input systems.
Given an arbitrary recursion-free CHC system $S$, \sys~generates an
equivalent CDD system $S'$ and solves $S'$ directly.
%
In general, $S'$ may have size exponential in the size of
$S$.
%
However, \sys~generates equivalent systems via heuristics analogous to
those used to generate compact verification conditions of hierarchical
programs~\cite{flanagan01,lal-qadeer15}.
%
In practice these heuristics often yield CDD systems which are
small with respect to the input system.
%
A general procedure for constructing a CDD expansion of a given CHC
system is given in \autoref{app:cons-cdd}.

>>>>

The hierarchy of discussed classes of recursion-free systems is
depicted in \autoref{fig:hierarchy}.
%
As shown, the class of CDD systems is a superclass of both the class
of body-disjoint systems and the class of linear systems. So any
recursion-free system that is efficiently expressible in body-disjoint
or linear form is also efficiently expressible in CDD form.
%
In addition, some systems which are expensive to express in
body-disjoint or linear form are efficiently expressible in CDD form.
%
\sys~takes advantage of this fact when solving input systems.
Given an arbitrary recursion-free CHC system $S$, \sys~reduce $S$ to an
CDD system $S'$ and solves $S'$ directly.
%
In general, $S'$ may have size exponential in the size of
$S$.
%
However, \sys~generates CDD systems via heuristics analogous to
those used to generate compact verification conditions of hierarchical
programs~\cite{flanagan01,lal-qadeer15}.
%
In practice these heuristics often yield CDD systems which are
small with respect to the input system.
%
A general procedure for constructing a CDD expansion of a given CHC
system is given in \autoref{app:cons-cdd}.
